Kvantni algebrajski učinki

### 2022-07-19 src/abstract.tex
Fixed polyglossia error
`en` is not recognized as a synonym for `english`,
despite what the documentation says

\abstract{
\begin{otherlanguage}{en}
    Quantum computation is based on many modern concepts in programming language theory,
    such as linear types, (quantum) physical phenomena, and many others.
    In this thesis we will be focusing just on these two.
    Our goal is to understand how quantum programs behave
    and a good way of understanding is understanding program equality.

>>>>

\abstract{
\begin{otherlanguage}{english}
    Quantum computation is based on many modern concepts in programming language theory,
    such as linear types, (quantum) physical phenomena, and many others.
    In this thesis we will be focusing just on these two.
    Our goal is to understand how quantum programs behave
    and a good way of understanding is understanding program equality.
